A Data-Driven Framework for Neural Field Modelling

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
Yet more comments
minor corrections

Figure~\ref{fig:Figure12} demonstrates the effect of the sigmoid parameters on the estimation accuracy. The RMSE of the reconstructed connectivity kernel was calculated for various parameters of the sigmoid by varying the slope, $\varsigma$, and the threshold, $v_0$. The other model parameters remained fixed and were set according the Table~\ref{tab:Parameters}.

@@

The isotropy of the connectivity kernel means that the mixing effect of the kernel on the firing rates can be written as a convolution of the kernel with the membrane voltage field basis functions. This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure10.pdf}
\end{center}
\caption{{\bf Examples of the actual and estimated neural fields and the error}. (\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data. (\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field. (\textbf{C}) The absolute error between the true and reconstructed fields. The error shows high frequency behaviour.}
\label{fig:Figure10}
\end{figure*}

>>>>

Figure~\ref{fig:Figure12} demonstrates the effect of the sigmoid parameters on the estimation accuracy. The RMSE of the reconstructed connectivity kernel was calculated for various parameters of the sigmoid by varying the slope, $\varsigma$, and the threshold, $v_0$. The other model parameters remained fixed and were set according to the Table~\ref{tab:Parameters}.

@@

The isotropy of the connectivity kernel basis functions means that the mixing effect of the kernel on the firing rates can be written as a convolution of the kernel with the membrane voltage field basis functions. This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure10.pdf}
\end{center}
\caption{{\bf Examples of the actual and estimated neural fields and the error}. (\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data. (\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field. (\textbf{C}) The error between the true and reconstructed fields. The error shows high frequency behaviour.}
\label{fig:Figure10}
\end{figure*}
